---
title: "R Notebook"
output: html_notebook
---

```{r}
if (!require("BiocManager", quietly = TRUE))
    install.packages("BiocManager")

BiocManager::install("AnnotationHub")
```

```{r}
if (!require("BiocManager", quietly = TRUE))
    install.packages("BiocManager")

BiocManager::install("clusterProfiler")
```


```{r}
install(clusterProfiler)



```
```{r}
if (!require("BiocManager", quietly = TRUE))
    install.packages("BiocManager")

BiocManager::install("org.Mm.eg.db")

library(org.Mm.eg.db)
```

```{r}
if (!require("BiocManager", quietly = TRUE))
    install.packages("BiocManager")

BiocManager::install("AnnotationHub")

library(AnnotationHub)
```

```{r}
ah <- AnnotationHub()

```

```{r}
query(ah, "OrgDb")
orgdb <- query(ah, c("OrgDb", "maintainer@bioconductor.org"))[[1]]
```

keytypes(orgdb)
columns(orgdb)
egid <- head(keys(orgdb, "ENTREZID"))
select(orgdb, egid, c("SYMBOL", "GENENAME"), "ENTREZID")

```{r}
library(msigdbr)
all_gene_sets <- msigdbr(species = "Mus musculus")
head(all_gene_sets)

```

```{r}
msigdbr_t2g = msigdbr_df %>% dplyr::distinct(gs_name, entrez_gene) %>% as.data.frame()
enricher(gene = gene_ids_vector, TERM2GENE = msigdbr_t2g, ...)
```


```{r}
#### enrichment
#Get gene set database

```

```{r}
library(enrichplot)

gseUP <- gseGO(geneList=genelist_UPREG_DENV2, 
             ont ="BP", 
             keyType = "SYMBOL", 
             nPerm = 10000, 
             minGSSize = 3, 
             #maxGSSize = 800, 
             pvalueCutoff = 0.05, 
             verbose = TRUE, 
             OrgDb = organism, 
             pAdjustMethod = "none")

gsePathway(, organism = "mouse", pvalueCutoff = 0.01)

upem <- emapplot(egoUP, showCategory = 10)
```

